### 2023-06-26 Draft.tex
Added conclusion to linear filtering

>>>>

With all the different kernels and each of their own applications, it is evident that even though linear filtering is fundamentally passing the weighted sum of a neighborhood, it can be a really powerful tool. Especially with today's hardware
linear filtering can be considered a quick and cost effective method for image processing.
